---
title: "Plotting and Analysis of AMS Data"
output: html_notebook
---

<p><em>Script by Nicolas Roberts</em></p>

<h2> Setup </h2>
<ul> 
<li> Set Working Directory </li>
<li> Load various libraries of functions </li>
</ul>
```{r}
setwd("~/Library/Mobile\ Documents/com~apple~CloudDocs/geologyGeometry")

# [!!!] FOR WINDOWS: Set the working directory.
# setwd("C:/users/[Insert user name]/Desktop/20170620geologyGeometry")

# Load the necessary R libraries.
source("library/all.R")
source("AMS_functions.R")
library("ggplot2")
library("ggforce")

library("imager")
library("gstat")
library("sp")
library("maptools")
library("rgdal")
library("png")
library("gridExtra")

library("chebpol")
library("sf")
library("viridis")


# library("gridExtra")
# library("grid")
# library("gtable")
# library("ggpubr")
#[!!!] Uncomment only if you have compiled C on your system and have the C libraries loaded at the top of this script. Uncomment and run the following line only if you have compiled C. # [!!!] Markov chain Monte Carlo and Kamb contouring in equal volume plots require C compiler. Skip MCMC and equal volume Kamb lines if you do not wish to install C. Load the necessary library
#source("libraryC/all.R")
```


<h2> Load AMS Data </h2>


<ul> 
<li> Import the AMS and location .csv files </li>
<li> Create a data frame of AMS data </li>
</ul>
```{r}
#Path to AGICO txt data file
AGICOcsvPath <- "data/pilbara/amsData_12Sept_2019.csv"



#USER MODIFY:
#the file path to the station name/location csv (see below for details on format)
locationPath <- "data/pilbara/sampleLocations.csv"


#load the AGICO csv file
dataFrame <- geoDataFromFile(AGICOcsvPath, separator = ",")

#This computes useful measures from the raw AGICO csv. This is the main variable which all the statistics will draw from. 
amsData <- geoEllipsoidDataFromAGICOFile(AGICOcsvPath, separator = ",", sapply(dataFrame$Km, function(s) s*10^(-6)), doNormalize=TRUE)
#for some reason, AGICO stores all the bulk susceptibilities as the actual susceptibility * 10^6, so this quickly corrects it.
amsData$Km <- sapply(amsData$Km, function(s) s*10^(-6))

#Loads a csv file with the location (easting, northing) information. The table needs to be formatted with headings "name", "easting", and "northing"--all lower case, no spaces. The table can include more stations than the amsData have, but must inlcude all stations in amsData. More details below. 
locData <- read.table(locationPath, sep = ",", header=TRUE,stringsAsFactors = FALSE)

```


```{r}
nameLength <- 9

#this calls the locationPairing function and apppends location data to the amsDataset. 
amsData <- locationPairing(amsData, locData, nameLength)
    
```

```{r}
ggsave("allAMSDataLineation.pdf", plotNet(amsData, showFollin = FALSE, whichAxes = "K1"))
ggsave("allAMSDataFoliation.pdf", plotNet(amsData, showFollin = TRUE, whichAxes = "K3"))
ggsave("allAMSHsu.pdf", plotHsu(amsData))
plotNetStation("AME16_105", amsData)
plotHsuStation("AME18_284", amsData)


plotNet(amsData, showFollin = FALSE, whichAxes = "K1")
plotNet(amsData, showFollin = TRUE, whichAxes = "K3")

plotHsuSummary = function(amsData) {
stationData <- amsData
logAs <- lapply(stationData$logA, function(ell) ell)



x <- function(logA) {-sqrt(1.5) * max(logA - sum(logA) / 3) - sqrt(1.5) * min(logA - sum(logA) / 3)}
y <- function(logA) {sqrt(0.5) * max(logA - sum(logA) / 3) - sqrt(0.5) * min(logA - sum(logA) / 3)}

lodes <- sapply(logAs, x)
oct <- sapply(logAs, y)

# the maximum octohedral shear strain
maxEs <- 0.5

# Dataframe that stores the Hsu Plot line segments that show lines of equal Lodes parameter
lines <- data.frame(x1 = c(0,0,0), 
                    x2 = c(maxEs*cos(pi/3),maxEs*cos(pi/2), maxEs*cos(2/3 * pi)),
                    y1 = c(0,0,0), 
                    y2 = c(maxEs*sin(pi/3), maxEs*sin(pi/2), maxEs*sin(2/3 * pi)),
                    label = c(1, 0, -1),
                    lineAlpha = c(1,.75,1)
)

# Make data frame of Hsu plot arcs of equal oct. shear strain
# Change arcInterval to have more or fewer arcs display on the Hsu plot
arcInterval = 0.2

arcs <- data.frame(
     start = rep(-pi/6, maxEs/arcInterval + 1),
     end = rep(pi/6, maxEs/arcInterval + 1),
     r = seq(from = 0, to = maxEs , by = arcInterval),
     textX = seq(from = 0*cos(pi/3), to = maxEs*cos(pi/3), by=arcInterval * cos(pi/3)),
     textY = seq(from = 0*sin(pi/3), to = maxEs*sin(pi/3), by=arcInterval * sin(pi/3))
)

#construct dataframe to plot
xy <- data.frame(cbind(oct, lodes))

#The Plot
HsuPlot <-ggplot() +
     coord_fixed(ratio = 1, ylim = c(-0.01,maxEs + 0.02), xlim = c(-maxEs/2 -0.01,maxEs/2 + 0.01)) +
     #plot the arcs and label them
     geom_arc(aes(x0 = 0, y0 = 0, r = r, start = start, end = end, alpha = 0.9), linetype = 1, color = "dark grey", data = arcs, show.legend = FALSE) +
     geom_text(aes(x=textX, y=textY,label = r,angle = -30), size = 2.75, family = "Helvetica", nudge_x = 0.01, nudge_y = -0.01, data = arcs)+
     geom_arc(aes(x0=0,y0=0, r= maxEs, start = - pi/6, end = pi/6), linetype = 1, show.legend = FALSE) +     
     #plot lines of equal lodes parameter and label them
     geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, alpha = lineAlpha), linetype = 1, data = lines, show.legend = FALSE) +
     geom_text(aes(x=x2, y=y2,label = label, vjust = -0.5, family = "Helvetica"), size = 2.75, data = lines) +
     #geom_text(aes(x=x, y=y, label = labels, angle = angle, family = "Times"), size = 2.75, data = axisLabels)+
     #plot data
     #stat_density2d(data = xy, aes(x= lodes, y = oct, fill = ..level..), geom = "polygon", n = 100)+
     geom_point(aes(x=lodes, y=oct), data = xy, size = 1, alpha = 0.3)+
     theme_void() +
     theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))

return(HsuPlot)
}

ggsave("plotHsuSummary.pdf", plot = plotHsuSummary(amsData), height = 4, width = 4, unit = "in")

```

```{r}

#compute 95% confidence bootstrap clouds
boots95 <- computeStationAMSBootStrap95("AME18_284", amsData)


plotBootstrapsHsu("AME18_284", amsData)


#plot 95% bootstrap clouds
plotNetBoots(amsData, "AME18_284")

# a list of station names for each core
stationList <- amsData$station

# Remove duplicate station names
stationList <- unique(stationList, incomparables = FALSE)

bootPlots <- computeAndPlotAllBootstraps(amsData, stationList, "AMS plots/equalAreaNets", "png")

```


```{r}

# a list of station names for each core
stationList <- amsData$station

# Remove duplicate station names
stationList <- unique(stationList, incomparables = FALSE)

amsDataMeans <- computeStationMeans(amsData, stationList)

ShapeVersusAnisotropy <- plotShapeVersusAnisotropy(amsData, gradient = "none")

ggsave("shapeVersusAnisotropy.pdf", plot = ShapeVersusAnisotropy)

plotHistogramLodes(amsDataMeans, binWidth = 0.2)


plotShapeVersusAnisotropyBootstraps("AME18_284", amsData)


# 

```


```{r}


index = which(amsDataMeans$Name == "AME18_147")
AME18_147 = amsDataMeans[index,]
ellEllipsoidPlot(AME18_147$rotation, AME18_147$a)
AME18_147
amsDataMeans

```


```{r}
#Load Geologic Map
shp <- read_sf("shapeFiles/1_500_000_Interpreted_Bedrock_Geology__2014.shp")     
shpCropped <- st_crop(shp, c(xmin=119.75, xmax=120.40, ymin=-21.50, ymax=-20.85))
granitoids <-shpCropped[shpCropped$SUPERSUITE != "NA",]
geoMap <- granitoids

figTree <- granitoids[granitoids$UNITNAME == "Fig Tree Gneiss",]
Joorina <- granitoids[granitoids$UNITNAME == "Joorina Granodiorite",]



#Call function to plot strikes and dips on in map view
mapStrikesAndDips <- plotMapStrikesDips(amsDataMeans, geoMap, onlyStat = FALSE)
mapStrikesAndDips

mapTrendsAndPlunges <- plotMapTrendsPlunges(amsDataMeans, geoMap)
mapTrendsAndPlunges

mapPlots <- plotMapPlots(amsDataMeans, geoMap, "AMS plots/equalAreaNets")
mapPlots

ggsave("Map_AMS_strikesAndDips.pdf", plot = mapStrikesAndDips)
ggsave("Map_AMS_trendsAndPlunges.pdf", plot = mapTrendsAndPlunges)
ggsave("Map_AMS_plots.pdf", plot = mapPlots, width = 20, height = 20, unit = "in")

#potasiumRaster <- raster("potasiumRaster.tif")

#plot(potasiumRaster)
```


```{r}
plotShapeVersusAnisotropy(amsData, gradient = "lodes")
plotShapeVersusAnisotropy(amsData, gradient = "oct")
plotShapeVersusAnisotropy(amsData, gradient = "Km")
plotShapeVersusAnisotropy(amsData, gradient = "none")

plotShapeVersusKm(amsData, gradient = "lodes")
plotShapeVersusKm(amsData, gradient = "oct")
plotShapeVersusKm(amsData, gradient = "Km")
shapeVersusKm <- plotShapeVersusKm(amsData, gradient = "none")

ggsave("shapeVersusKm.pdf", shapeVersusKm)

```


```{R}
     shp <- read_sf("shapeFiles/1_500_000_Interpreted_Bedrock_Geology__2014.shp")
     shp2 <- st_read("shapeFiles/1_500_000_Interpreted_Bedrock_Geology__2014.shp")
     

     # Just plot the geometry
     plot(st_geometry(shp))
     
     # Plot geometry colored categorically ( I think arbitrarily)
     plot(st_geometry(shp), col = sf.colors(12, categorical = TRUE), border = 'grey', axes = TRUE)
     
     # Crop the shape file to a rectangle
     
     
     # Use ggplot natively to make more specific plots!     
     ggplot(shpCropped["SUPERSUITE"]) +
          geom_sf(aes(fill = SUPERSUITE)
     
    
     
     shp <- read_sf("shapeFiles/1_500_000_Interpreted_Bedrock_Geology__2014.shp")     
     
     shpCropped <- st_crop(shp, c(xmin=119.75, xmax=120.40, ymin=-21.50, ymax=-20.85))
     
     granitoids <-shpCropped[shpCropped$SUPERSUITE != "NA",]
     
    blankMap =  ggplot(granitoids["SUPERSUITE"]) +
          geom_sf(aes(fill = SUPERSUITE)) +
          coord_sf(ylim=c(-20.85,-21.5),xlim=c(119.75,120.4), expand = FALSE) +
          scale_fill_manual(values=c("Split Rock Supersuite" = "#F77D84", "Cleland Supersuite" = "#EEC0DA", "Emu Pool Supersuite" = "#E49DC5", "Tambina Supersuite" = "#DA78B1", "Callina Supersuite" = "#D557AC")) +
          theme_bw()
     
    
     ggsave("blankMtEdgar.pdf", blankMap)
```




```{r}
shp <- read_sf("shapeFiles/1_500_000_Interpreted_Bedrock_Geology__2014.shp")     
     shpCropped <- st_crop(shp, c(xmin=119.75, xmax=120.40, ymin=-21.50, ymax=-20.85))
     granitoids <-shpCropped[shpCropped$SUPERSUITE != "NA",]


geoMap <- granitoids

mapLodes <- plotMapByProperty(amsDataMeans, property = "lodes", geoMap)

mapLodes
ggsave("mapLodes.pdf", mapLodes )

plotMapByProperty(amsDataMeans, property = "oct", geoMap)
mapKm <- plotMapByProperty(amsDataMeans, property = "Km", geoMap)
mapKm
ggsave("mapKm.pdf", mapKm)

ggsave("mapStations.pdf", plotMapByProperty(amsDataMeans, property = "none", geoMap))

plotOctVersusKm(amsData, gradient = "lodes")
plotOctVersusKm(amsData, gradient = "oct")
plotOctVersusKm(amsData, gradient = "Km")
plotOctVersusKm(amsData, gradient = "none")

plotLodesVersusKm(amsData, gradient = "lodes")
plotLodesVersusKm(amsData, gradient = "oct")
plotLodesVersusKm(amsData, gradient = "Km")
plotLodesVersusKm(amsData, gradient = "none")


?# ggsave("Strikes and Dips.pdf", plot2Save, device = "pdf", width = 20, height = 20, units = "in", dpi = 300)
```

```{r}
coords <- cbind(geoMap$long, geoMap$lat)
box <- bbox(coords)

map <- SpatialPoints(data.frame(geoMap$long, geoMap$lat))
interpData <- SpatialPointsDataFrame(data.frame(amsDataMeans$easting, amsDataMeans$northing), data.frame(log10(amsDataMeans$Km)), bbox = box)

####

library(spatstat)  # Used for the dirichlet tessellation function
library(maptools)  # Used for conversion from SPDF to ppp
library(raster)    # Used to clip out thiessen polygons
library(tmap)

# Create a tessellated surface
th  <-  as(dirichlet(as.ppp(interpData)), "SpatialPolygons")

# The dirichlet function does not carry over projection information
# requiring that this information be added manually
proj4string(th) <- proj4string(interpData)

# The tessellated surface does not store attribute information
# from the point data layer. We'll use the over() function (from the sp
# package) to join the point attributes to the tesselated surface via
# a spatial join. The over() function creates a dataframe that will need to
# be added to the `th` object thus creating a SpatialPolygonsDataFrame object
th.z     <- over(th, interpData, fn=mean)
th.spdf  <-  SpatialPolygonsDataFrame(th, th.z)

# Finally, we'll clip the tessellated  surface to the Texas boundaries
#th.clp   <- raster::intersect(map,th.spdf)

# Map the data


tm_shape(th) + 
  tm_polygons(col="Precip_in", palette="RdBu", auto.palette.mapping=FALSE,
              title="Predicted precipitation \n(in inches)") +
  tm_legend(legend.outside=TRUE)
```

```{r}

amsDataMeansLocs <- list()
for (i in 1:length(amsDataMeans$Name)){
     amsDataMeansLocs[[i]] <- c(amsDataMeans$easting, amsDataMeans$northing)
}

array <- sapply(amsDataMeans$vector, function(s) s)

test <- ipol(val = array, grid = amsDataMeansLocs)

s <- seq(-20,-22,length.out = 100)
e <- seq(-119, -121, length.out = 100)

locs <- cbind(s,e)

vals <- cbind(s, e, sapply(locs, function(c) test(c(locs[1], locs[2]))))

```
```{r}
#Variogram analysis of strike
dataSet <- amsDataMeans


sd <- lapply(dataSet$rotation, function(s) geoStrikeDipDegFromCartesian(s[3,]))

distanceAndAngle <- list()
count = 1

for ( i in 1:length(dataSet$Name)) {
     if (i < length(dataSet$Name)){
     for (j in i+1:length(dataSet$Name)){
          distance <- ((dataSet$easting[i] - dataSet$easting[j])^2 + (dataSet$northing[i] - dataSet$northing[j])^2)^(1/2)
          angle1 <- max(c(sd[[i]][1], sd[[j]][1]))
          angle2 <- min(c(sd[[i]][1], sd[[j]][1]))
          angleDiff <- angle1 - angle2
          if (angleDiff > 180) {
               angle1 <- angle1 - 180
               angleDiff <- angle1 - angle2
          }
          if (angleDiff > 90) {
               angleDiff <- 180 - angleDiff
          }
     }
     }
          
          print(angleDiff)
          
          vari <- (angleDiff/2)^2
          distanceAndAngle[[count]] <- c(distance, vari) 
          count = count + 1
          
          
     
     }
}

distances <- sapply(distanceAndAngle, function(s) (s[1]))
angles <- sapply(distanceAndAngle, function(s) (s[2]))

angDists <- data.frame(cbind(distances, angles))

ggplot(angDists) +
     geom_point(aes(x=distances, y= angles)) +
     coord_cartesian(xlim = c(0,.25))

plot(distances, angles)

```
```{r}
ellipsoids <- amsDataMeans$rotation
as <- amsDataMeans$a
easting <- amsDataMeans$easting
northing <- amsDataMeans$northing
location <- list()

for (i in 1:length(easting)) {
     location[[i]] <- c(easting[i], northing[i], 0)
}

ellEllipsoidPlot(ellipsoids, as, centers=location )

#xmin=119.75, xmax=120.40, ymin=-21.50, ymax=-20.85)

```
```{r}
dataSet = amsDataMeans

station = dataSet$Name
easting = dataSet$easting
northing = dataSet$northing
sd = lapply(dataSet$rotation, function(s) geoStrikeDipDegFromCartesian(s[3,]))
strike = sapply(sd, function(s) s[1])
dip = sapply(sd, function(s) s[2])
tp = lapply(dataSet$rotation, function(s) geoTrendPlungeDegFromCartesian(lower(s[1,])))
trend = sapply(tp, function(s) s[1])
plunge = sapply(tp, function(s) s[2])
lodes = sapply(dataSet$logA, function(s) ellLodeNu(s))
oct = sapply(dataSet$logA, function(s) ellOctahedralShearStrain(s))
Km = sapply(dataSet$Km, function(s) log10(s))



dataFrameForExport <- data.frame(station, easting, northing, strike, dip, trend, plunge, lodes, oct, Km, stringsAsFactors = FALSE)

write.table(dataFrameForExport, "test.csv", sep = ",")
```

```{r}

easting = dataSet$easting
northing = dataSet$northing
down = replicate(length(dataSet$northing), 0)
xyz = lapply(dataSet$rotation, function(s) lower(s[1,]))
x = sapply(xyz, function(s) s[1])
y = sapply(xyz, function(s) s[2])
z = sapply(xyz, function(s) s[3])

dataFrameQuiver = data.frame(easting, northing,down,x,y,z)
write.table(dataFrameQuiver, "quiverLines.csv", sep = ",", row.names = FALSE)


```
```{r}

ellEllipsoidPlot(list(rbind(c(1,0,0),c(0,1,0),c(0,0,1))), 
                 list(c(2,0.2,0.2)),
                 axesColor = c("black","black","black"),
backgroundColor="white", curveColor="black")

afterMaximizingWindow(rightName = "ProlateEllipsoid.png", zoom = 0.7)


ellEllipsoidPlot(list(rbind(c(1,0,0),c(0,1,0),c(0,0,1))), 
                 list(c(0.3,1.5,1.5)),
                 axesColor = c("black","black","black"),
backgroundColor="white", curveColor="black")

afterMaximizingWindow(leftName = "OblateEllipsoid.png", zoom = 0.7)

ellEllipsoidPlot(list(rbind(c(1,0,0),c(0,1,0),c(0,0,1))), 
                 list(c(2,1,1/2)),
                 axesColor = c("black","black","black"),
backgroundColor="white", curveColor="black")

afterMaximizingWindow(leftName = "TriaxialEllipsoid.png", zoom = 0.7)

```

```{r}
namesNorthLimb = c( "AME16_140", "AME18_114", "AME18_117", "AME18_116") 
                   
                   #"AME19_093", "AME16_094", "AME16_097", "AME16_095", "AME16_096","AME18_018", "AME18_017")

namesSouthLimb = c("AME18_104", "AME16_141", "AME18_015", "AME16_139", "AME18_111", "AME16_138", "AME18_242", "AME16_137")

subsetData <- function(amsData,stationNames) {
     amsData_subset = stationDataSubset(stationNames[1], amsData)
     for (i in 2:length(stationNames)){
          amsData_subset = rbind(amsData_subset, stationDataSubset(stationNames[i], amsData))
     }
     return(amsData_subset)
}

amsDataNorthLimb <- subsetData(amsData, namesNorthLimb)

amsDataSouthLimb <- subsetData(amsData, namesSouthLimb)


ggsave("northLimbNet.pdf", plotNet(amsDataNorthLimb, showFollin = TRUE), height = 4, width = 4, unit = "in")
ggsave("southLimbNet.pdf",plotNet(amsDataSouthLimb, showFollin = TRUE),height = 4, width = 4, unit = "in")

allFold = rbind(amsDataNorthLimb, amsDataSouthLimb)

ggsave("FoldHsuSummary.pdf", plotHsuSummary(allFold), height = 4, width = 4, unit = "in")

plotNetBootsAll(amsDataNorthLimb)
plotNetBootsAll(amsDataSouthLimb)

bootsDataNorth <- computeAMSBootStrap95(amsDataNorthLimb)
bootsDataSouth <- computeAMSBootStrap95(amsDataSouthLimb)

oriEqualVolumePlot(group = oriLineInPlaneGroup,  c(bootsDataNorth$rotation, bootsDataSouth$rotation), col = c(replicate(length(bootsDataNorth$rotation), "white"), replicate(length(bootsDataSouth$rotation), "blue")))


northMean <- ellMean(bootsDataNorth$vector)
northLineation <- northMean$rotation[3,]

lineEqualAreaPlot(list(northLineation))

southMean <- ellMean(bootsDataSouth$vector)
southLineation <- southMean$rotation[3,]

lineEqualAreaPlotTwo(list(northLineation), list(southLineation))

foldAxis = cross(southLineation, northLineation)

geoTrendPlungeDegFromCartesian(lower(foldAxis))

lineEqualAreaPlotThree(list(northLineation), list(southLineation), list(foldAxis))

```

```{r}

transect <- c("AME18_145",
              "AME18_146",
              "AME18_147",
              "AME18_149",
              "AME18_159",
              "AME18_156",
              "AME18_155")

transectData = subsetData(amsData, transect)

oriEqualVolumePlot(group = oriLineInPlaneGroup, c(transectData$rotation), col = hues(as.numeric(transectData$northing)))

lines <- lapply(transectData$rotation, function(S) S[1,])

lineEqualAreaPlot(lines, col = hues(as.numeric(transectData$northing)))

oriGeodesicRegression(as.numeric(transectData$northing),transectData$rotation, oriLineInPlaneGroup, numSteps = 1000)




```
```{r}

nose = c("AME18_018",
         "AME16_142",
         "AME16_144",
         "AME18_020")

noseBridge = c("AME18_120",
         "AME18_092",
         "AME16_091",
         "AME18_165",
         "AME18_167",
         "AME16_090",
         "AME18_168",
         "AME18_131")

noseData = subsetData(amsData, nose)

ggsave("noseMtEdgar.pdf", plotNet(noseData, showFollin = FALSE), height = 4, width = 4, unit = "in")

ggsave("noseHsu.pdf", plotHsu(noseData),height = 4, width = 4, unit = "in")

noseBridgeData = subsetData(amsData, noseBridge)

ggsave("noseBridgeMtEdgar.pdf", plotNet(noseBridgeData, showFollin = FALSE), height = 4, width = 4, unit = "in")

ggsave("noseBridgeHsu.pdf", plotHsu(noseBridgeData),height = 4, width = 4, unit = "in")


shp <- read_sf("shapeFiles/1_500_000_Interpreted_Bedrock_Geology__2014.shp")     
     shpNose <- st_crop(shp, c(xmin=119.8719, xmax=120.0999, ymin=-21.3418, ymax=-21.1836))
     noseGranitoids <-shpNose[shpNose$SUPERSUITE != "NA",]

nosePlanesMap <- plotMapStrikesDips(amsDataMeans, shpNose, onlyStat = FALSE , xlims = c(119.8719,120.0999), ylims =  c(-21.3418,-21.1836))

noseLinesMap <- plotMapTrendsPlunges(amsDataMeans, shpNose , xlims = c(119.8719,120.0999), ylims =  c(-21.3418,-21.1836), size = "small")

ggsave("noseMapPlane.pdf", nosePlanesMap, useDingbats = FALSE)
ggsave("noseMapLines.pdf", noseLinesMap, useDingbats = FALSE)

```

```{r}

FigTree = c("AME16_145", "AME16_089", "AME16_078","AME16_077", "AME16_076", "AME16_075", "AME16_146","AME18_265")

subsetData <- function(amsData,stationNames) {
     amsData_subset = stationDataSubset(stationNames[1], amsData)
     for (i in 2:length(stationNames)){
          amsData_subset = rbind(amsData_subset, stationDataSubset(stationNames[i], amsData))
     }
     return(amsData_subset)
}

amsDataFigTree <- subsetData(amsData, FigTree)


ggsave("FigTreeNet.pdf", plotNet(amsDataFigTree, showFollin = TRUE), height = 4, width = 4, unit = "in")


ggsave("FigTreeHsuSummary.pdf", plotHsuSummary(amsDataFigTree), height = 4, width = 4, unit = "in")

```

```{r}

FigTree2 = c("AME16_032","AME16_033","AME16_034","AME16_035","AME16_055")

amsDataFigTree2 <- subsetData(amsData, FigTree2)


ggsave("FigTreeNet2.pdf", plotNet(amsDataFigTree2, showFollin = TRUE), height = 4, width = 4, unit = "in")


ggsave("FigTree2HsuSummary.pdf", plotHsuSummary(amsDataFigTree2), height = 4, width = 4, unit = "in")

```

```{r}

BishopCreek <- c("AME18_148","AME18_149","AME18_159","AME18_156", "AME18_147","AME18_146","AME18_155","AME18_154", "AME18_152", "AME18_151","AME16_083")

amsDataBishopCreek <- subsetData(amsData, BishopCreek)


ggsave("BishopCreeekNet.pdf", plotNet(amsDataBishopCreek, showFollin = FALSE), height = 4, width = 4, unit = "in")


ggsave("BishopCreekHsuSummary.pdf", plotHsuSummary(amsDataBishopCreek), height = 4, width = 4, unit = "in")

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

